\section{Different cultural backgrounds}
In a group with individuals from different countries it is important to take into consideration that there are many different cultural aspects and that it is important to learn a little bit about each other when working so close together.
The main body of knowledge about the culture and persona of the team members has so far been learned during the check-in activities in the morning of Village days.

During the Village check-in activities of February 9, a large cultural difference between the group members was discovered.
As we were discussing our favourite colours,
Arash said his favourite colour was green while Victor later told us that green is associated with infidelity in his country.
If a wife cheats on her husband, the husband is said to wear a green hat.
Arash replied that they have the same expression in Iran only they use the colour red.
The Norwegians in the group had no recollection of a similar expression used in Norway.

In accordance with [Scwartz] ground rule number 2 this is a very important part of the process, since not only the technological background is important when making decisions, but also the manner in which it is presented.
Knowledge about other group members could lead to a quicker decision-making process since it might reduce the frequency of misunderstandings in communication.
Later in the semester it was made clear to us that ... % I'm uncertain what was intended here.

\section{The Situation}
On the February 9 one of Schwartz ground rules for effective teamwork was broken by group members, resulting in an escalated Situation.
Although the need arose, talking openly about potentially hard or uncomfortable issues, so called undiscussable issues, was not initiated.
This happened during a discussion session about the specific goals in our project.
Arash drew a schematic illustrating the project and focusing heavily on his favoured part in the project, the signal processing.
A couple of days later there was posted a note on ``It's learning'' from Andreas that he was sick of Arash not including his part in the project, as he felt it necessary according to [Schwartz] rule number 4. % Should rewrite.
Arash replied 22 hours later that he was surprised reading the note, and claimed never to have intentionally agitated the other members, and was open to the opinion of others as exemplified in this quote from his reply:
\begin{quote}
  (...)~I think every body can tell his or her opinion exactly when think  it is wrong,~(...)
\end{quote}

The next meeting was as usual on Wednesday at 9 and we were not sure beforehand how the atmosphere in the group would be due to the posts.
After the mandatory activities we decided to talk openly about the problems in the group, as the current environment was non-conducive to productivity.
Both Andreas and Arash were called upon to explain their respective stories, which eventually solved the conflict as the group analysed the different views and converged on a project scope.
Conflict in a group is not necessary a negative thing as long as we turn it into an experience we can learn something from and use it to improve the co-operation in the team.

We found this application of [Schwartz]' rules of cooperation to greatly enhance our level of cooperation, as it enabled us to remove this obstacle while still maintaining trajectory.

\section{Telephone list}
When visiting the EMG lab the team got separated into two groups, due to there being many students present at the introduction.
After the main introduction was completed, Andreas, Erik and Victor stayed to ask a few questions and obtain information from Professor Øyvind.
Arash and Kristine did not notice this turn of events, as they were lost in the deluge of students emerging from the laboratory to attend a different lecture in the basement.
Kristine and Arash returned to the classroom in the basement and waited for the other three.

After a while they grew worried, and went looking for the rest but could not find them.
Kristine eventually returned to the basement and found the rest of the group attending the lecture, but Arash didn't return until much later.

To avoid repeating this kind of mishap in the future, we decided to create a list over the group member's phone numbers, so it will be possible to reach the individual members if such should be necessary.
This has saved time on later occasions, for example as Erik and Kristine met for the initial outline meeting for work on the process report without pre-emptively agreeing on a meeting location.

\section{EMG equipment}
The team had a few difficulties with using the EMG equipment, and was not able to begin experiments including the signals until two weeks after the original plan.
This was mostly due to faulty and/or missing equipment.
The first time the power supply of the computer was broken, as it had been during the introduction to EMG.
Thus, it had to be handed in for repair.
The second time, the computer was back from repair but lacked the necessary software for signal acquisition.
This led to some frustration in the group and we felt that the progress of the project was going to slow.
The delay with the EMG signal resulted in a slight change in the project, proposed by Prof. Øyvind.
We decided to avoid further EMG acquisition problems by basing the project on AMG and developing our own acquisition equipment.
This was to prevent the group from lacking work and produced a task that was a bit different in the signal acquisition part but where the signal processing would be almost the same.

\section{Introducing AMG}
We decided to try to complete the project with openings for both EMG and AMG, as most parts of the work will not be specific to one or the other.
This gives the lucrative property that if one of the goals regarding the EMG or AMG fails, then the group can fall back on the other plan.
The group also decided to continue with both projects in parallel to make sure that all group members have something to do at all times, as the EMG signals were already available while the AMG device had to be built.
%Although all the group members have decided to try to finish both parts since AMG is a newer research.

\section{Group form}
During the meeting on February 02, the group filled out forms concerning the dynamics of the group.
It was clear that there were some disagreements, especially regarding the communication between the members and some members being of the opinion that the project goal was unclear.
After a quick discussion, the group stated that the reason the answers were different, at least regarding the goals for the project, was that the goals have changed a bit along the way.
As such, the goals have changed, and different opinions about how the question wording should e interpreted resulted in different answers.
An example of such a change is the change from just studying EMG to including AMG as well.
This change made a big impact on the acquisition part of the project, since the signals (respectively; electric and acoustic) are acquired with vastly different equipment, resulting in two very different designs.

The other area of deviation in opinion was between Arash and the rest of the group.
As he worded it in the group log of the week:
\begin{quote}
  I thought the answers to them should be better!
\end{quote}
% The largest deviation about the communication was between Arash and the rest of the group and like he presented in his group log contribution that week: "I thought the answers to them should be better!"
A reason for this might be that he is one of the parts in most of the discussions where the communication fails.
This was later brought up at the log feed-back meeting with the village student assistants (Miss Marie and Miss Marianne), and after some discussion the group decided to better explaining our views, especially regarding the project direction and goals to alleviate further polarisation.
It was also suggested that the language barrier might be a large part of this issue.
%And that the reason for these break-downs in communication is perhaps due to a different technological background and the fact that the English is slightly different in pronunciation in the different countries and the fact that everyone in our group most communicate in their second language.

\section{Project}
When performing the signal acquisition, goal 1 of the EMG part, there were four of five members on the EMG lab.
The initial plan of reusing parts of a previous project was thwarted by the non-existence of such.
Erik, having prior experience with the acquisition software, was chosen to implement the signal acquisition to the direction of Arash's, who had knowledge about the EMG signal and the following processing.
The others in the group watched the work for the most of the time and although this was not the most efficient work method, this is a central part of the project and it is therefore important to know most of the details regarding the different parts of the project.

\section*{Might be worth to add at some piubt}
\begin{itemize}
  \item We decided against agendae.
\end{itemize}
