%!TEX TS−program = xetex
%!TEX encoding = UTF−8 Unicode
\documentclass[a4paper, oneside, fleqn, halfparskip]{scrartcl}
\usepackage{amssymb}
\usepackage{amsbsy}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{undertilde}
\usepackage{xunicode}
\usepackage{fontspec}
\usepackage{xltxtra}
\usepackage{polyglossia}
\setmainlanguage{english}
\setromanfont[Mapping=tex-text]{Linux Libertine O}
\setsansfont[Mapping=tex-text]{Linux Biolinum O}
\setmonofont[Mapping=tex-text, Scale=0.8]{DejaVu Sans Mono}
% \setmonofont[Mapping=tex-text, Scale=0.9]{Courier New}
%\setromanfont[Mapping=tex-text]{Times New Roman}
%\setromanfont[Mapping=tex-text]{Arial}
\usepackage{units}
\usepackage{wasysym}
\usepackage{graphicx}
\usepackage{float}
\usepackage{color}
% \usepackage{transparent}
\usepackage{listings}

\renewcommand{\labelenumi}{\alph{enumi})}
\renewcommand{\labelenumii}{\roman{enumii})}
%\renewcommand{\vec}[1]{\ensuremath{\mathbf{#1}}} % for vectors
\renewcommand{\vec}[1]{\ensuremath{\boldsymbol{#1}}} % for vectors
\newcommand{\mat}[1]{\ensuremath{\utilde{#1}}} % for matrices
\newcommand{\curl}[1]{\ensuremath{\mathbf{\nabla} \times #1}} % 
\newcommand{\abs}[1]{\ensuremath{\left| #1 \right|}} % 
\newcommand{\re}[1]{\ensuremath{\text{Re}\left\{ #1 \right\}}} % 
\renewcommand{\exp}[1]{\ensuremath{\text{e}^{ #1 }}} % 
\newcommand{\fact}{\emph{citation needed}} % 
% \def\svgwidth{5cm}
% \def\unitlength{10cm}
\begin{document}
\title{Procrep}
\subject{Homo Mobilis — Eksperter i Team}
\author{Erik Moen — Fantastic 4.}
\maketitle
%\tableofcontents

\section{In the beginning}
% [We didn't have a group]

More focus on:
- How interaction worked.
- Intra-group work presentations. (De er pådrag!)

\section{Week one}
%[Culture Dialogue.]

Subject dialogue
- list important factors
As instructed by the facilitartors, we started mapping our areas of knowledge on large posters, in order to find our individual and collctive strong and weak areas.

- Presenting the EMG idea
During the session Mr. Arash made his initial presentation of an idea concerning diagnotisation of patients using electromyography (EMG), which appeared to fit the group particularly well in addition to providing a new and challenging field for the participants. 

While other project ideas were discussed, we all believed this EMG idea would be our actual subject. [[CHECK]]

Discussion on teamwork
As a start on the creation of the team cooperation agreement we were instructed to concider and discuss what we wanted or wanted to avoid in the cooperation, in particular factors that helped create a good cooperation environment.
- [[List of key items chosen (I think there is a large paper)]]

% After finding common ground form this discussion, key items were documented and turned into a draft agreement. The following were adressed.
% - Leader (w/ responsibilities)
% - Decision method
% - Frequencies for meetings
% - Task distribution
% - Absence
% - [[argumentation]]

% - [[Reason for team contract]]
The team cooperation agreement is particularly usefull when people of different backgrounds are to cooperate, as it can form a common base to build the rest of the cooperation on. It also enables us to have a common reference as baseline for expectations from each other.

[[Important concepts included, with theory.]]
Of particular interest, the contents of the cooperation agreement describe our choice of goals, group leader style and responsibilities, method of making decisions, work division and feedback to the rest of the group. In addition it designates a head communicator, Miss. Kristine, who will help with difficulties in communication.

According to [[Sz:2002]] the method of making decisions in a group is a trade-off between efficiency and internal acceptance of the decisions made. We came to the conclusion (by full consensus) that a simple, informed majority is sufficient for decisions within the group, while the other methods discussed included full consensus and external arbitration. 

We decided to have a leader and rotate the position according to a static, repeating roster. This rotation enabled us to give the leader resonsibility for the completion of weekly tasks like creation of group logs outside of the meetings proper.

It was decided to attempt to divide the work on the two reports in two focus teams, where each team has the responsibility for one report, while taking input from the other.

\section{The second week}
%[Project rprt lect.]
%[Library]

Rectification of C.ag'mnt.
Importance of rectification?

Continuing the process of creating the team cooperation agreement, the draft agreement was reviewed. Imprecisions and contested sections were corrected to everyones satisfaction and previously omitted paragraphs were added. 

\paragraph{The choice of subject}
Before work could start, the group members had to agree on a project subject \fact. A session was held where the members attempted to find a subject to fit as well as possible to the criteria spec'd by the EiT village. 

%- What do we do!!
One of the criteria for a subject is to include the professional field of every member and exploit the available diversity. The discussion would thus be greatly helped by every participant knowing the field of study for the others, according to [rule 1]. Thus, we all spoke a bit about what our topics of study were. This application of theory greatly helped the discussion, and opened our eyes to new angles to include all of our areas of expertise.

The discussion lead us to further support of the EMG diagnostisation project, as it was found to both examplify the village theme and be simple to incorporate features examplifying our various areas of expertise. In addition to the signal processing (Arash' specialty), it can include a distribution component to take advantage of Victor's network expertise. The aquisition of the EMG from a patient is within the field of both Erik and Kristine, and once aquired the EMG signal can also be used in usefull cybernetic applications, Andreas' specialty. 

The subject also examplifies the village theme, \emph{Homo Mobilis}, by being based on the processes in one of the building stones of human movement, the muscles. 

[[check date, might be next week]]Before we left the village that day, we made a formal decision to have EMG as our project subject, in accordance with the procedure agreed upon in the cooperation agreement.

\section{La troisième semaine}
%Plane crash
The day started with a Check-in activity, where we individually rated items after their utility for keeping the group alive after a plane crash in winter in northern Canada. Afterwards we had a discussion within the group and decided (in accordance with our coop.ag'mnt) on a group answer. 

During this activity, we found that member participation varies between our group members, and (with the help of a \emph{sociogram} made by Miss Marie) interaction is better between some group members than others and some apparent polarization where some members communicated better/more than others. This fact was decomposed into a number of causes:
\begin{itemize}
  \item Good communication between participants with similar background, in particular Erik and Andreas.
  \item Different comittment to the task. In particular Arash concidered the task to be off-topic, and thus didn't want to engage in a demanding debate over the choices.
\end{itemize}
This helped us identify a need to knit the group more tightly together. Andreas suggested we attempt to take control over the situation by collecting the group for the upcoming luncheon. This suggestion fell through, partly because the intention was not communicated with sufficient fidelity.



%Café dialogue



[Chinese new year]
Due to the exact date of this village day, we were presented with a special concideration. The start of the Chinese New Year's celebrations caused Mr. Victor to wish to be excused from the group for the afternoon. It was unanimously decided that such cultural happenings should mandate absence from the group without penalty.

%Buildup to different opinions of our project's goals. (With following steering on behalf of Andreas)
%- Polarisation between Andreas and Arash.
%- Compounded by café dialogue.

Andreas felt action was needed while reviewing the day, and posted the appended note to the group, according to [rule 4] regarding ``open cards.'' [[I understand K. has detailed this]]

- Arranged to be taken to the EMG-lab next week.
- Important to get better understanding of both the available equipment and expertise, and to get a fuller understanding of the subject that is EMG. 

\section{Closing words}

\input{part2.tex}
\end{document}
