%!TEX TS−program = xetex
%!TEX encoding = UTF−8 Unicode
\documentclass[a4paper, oneside, fleqn]{scrartcl}
\usepackage{amssymb}
\usepackage{amsbsy}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{undertilde}
\usepackage{xunicode}
\usepackage{fontspec}
\usepackage{xltxtra}
\usepackage{polyglossia}
\setmainlanguage{english}
\setromanfont[Mapping=tex-text]{Linux Libertine O}
\setsansfont[Mapping=tex-text]{Linux Biolinum O}
\setmonofont[Mapping=tex-text, Scale=0.8]{DejaVu Sans Mono}
% \setmonofont[Mapping=tex-text, Scale=0.9]{Courier New}
%\setromanfont[Mapping=tex-text]{Times New Roman}
%\setromanfont[Mapping=tex-text]{Arial}
\usepackage{units}
\usepackage{graphicx}
\usepackage{float}
\usepackage{color}
% \usepackage{transparent}
\usepackage{listings}

\renewcommand{\labelenumi}{\alph{enumi})}
\renewcommand{\labelenumii}{\roman{enumii})}
%\renewcommand{\vec}[1]{\ensuremath{\mathbf{#1}}} % for vectors
\renewcommand{\vec}[1]{\ensuremath{\boldsymbol{#1}}} % for vectors
\newcommand{\mat}[1]{\ensuremath{\utilde{#1}}} % for matrices
\newcommand{\curl}[1]{\ensuremath{\mathbf{\nabla} \times #1}} % 
\newcommand{\abs}[1]{\ensuremath{\left| #1 \right|}} % 
\newcommand{\re}[1]{\ensuremath{\text{Re}\left\{ #1 \right\}}} % 
\renewcommand{\exp}[1]{\ensuremath{\text{e}^{ #1 }}} % 
% \def\svgwidth{5cm}
% \def\unitlength{10cm}
\begin{document}
\title{Cooperation Agreement}
\subject{Homo Mobilis — Eksperter i Team}
\author{Erik Moen — Fantastic 4.}
\maketitle
\section*{Group participants}
\begin{itemize}
  \item SHAHMANSOORI, Arash
  \item NORDAL, Andreas
  \item MOEN, Erik
  \item BREITEIG, Kristine
  \item ZHANO, Haijiao
\end{itemize}

\section*{Agreements}

\subsection*{Practical}
\paragraph{Workload}
Workload should be about 10 hours per week, or approximately 5 hours plus the mandatory meeting.

\paragraph{Meetings}
Mandatory participation on weekly meetings in the basement of the Elektro-building every Wednesday at 9.

Everyone will be on time at planned meetings, any absence must be announced. Electronic mail is a suggested method of making this announcement.

\paragraph{Structure}
We will have ``subdeadlines'' along the way as we work.

Tasks will be divided amond the group members, who will report their progress to the rest of the group at weekly meetings.

Any problems completing assigned tasks must be communicated to the group in order to compensate or give feedback. The leader will follow up the tasks.

\subsection*{Process}
\paragraph{Leader}
The group will have a leader. The leader changes every week, starting week 4. Leadership is rotated through the list of group participants sorted by given name.

The leader shall:
\begin{itemize}
  \item Facilitate cooperation
  \item Lead meetings
  \item Arrange meetings
  \item Lead decisionmaking
\end{itemize}

\paragraph{Decisions}
Decisions within the group can be made by majority vote.



\end{document}
